pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-28 article.tex
Better caption for fig 1

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    pirouette pipeline
  }
  \label{fig:pipeline}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a true phylogeny (1a), 
    that is converted to an alignment (2a), which is used
    to create a BEAST2 posterior of phylogenies (3a),
    which is compared to the true phylogeny (1a) using
    the nLTT statistic. (4a) shows the nLTT of the true tree in red,
    the nLTT of all individual posterior trees in grey, and the average
    nLTT statistic of all posterior trees in black.
    Taking the differences between the true tree's nLTT and each posterior's
    nLTT results in an error distribution, here displayed as a histogram
    of error values (5a).
    Optionally, a twin phylogeny (1b) can be generated from a true
    phylogeny (1a), which then results in an error distribution (5b) with
    the similar intermediate steps 
  }
  \label{fig:pipeline}
\end{figure}
